---
title: "Effect of skin tone on device performance"
author: "Rebecca Green"
date: "`r Sys.Date()`"
output: 
  word_document:
    reference_docx: template_formatted.docx
---

```{r setup, include=FALSE}
rm(list = ls())

# Rmd setup (since we echo all code)
knitr::opts_chunk$set(echo = FALSE)

# install these packages if not already on your computer
library(plyr)
library(dplyr)
library(reshape2)
library(ggplot2)
library(stargazer)
library(lme4)

# Read in (cleaned) data 
filename <- "C:/Users/rgreen/Box/3_Output 3/Hybrid study/Diagnostic accuracy study/Analysis/dx-accuracy-data_clean_2024-03-28.csv" #primary analysis
df_og <- read.csv(filename)
df_og <- df_og %>% select(-c("X", "m1_index_temp_f", "m2_index_temp_f", "m3_index_temp_f"))

# Exclude colorimeter readings out of range (only saw in b)
df_og$colorimeter_b <- ifelse(df_og$colorimeter_b>127, NA, df_og$colorimeter_b)
# Calculate ITA from colorimeter measures
df_og$ita <- (atan(df_og$colorimeter_l-50)/df_og$colorimeter_b)*(180/pi)

# Step 1: Reshape to create long df
## use regular expressions to identify measurement-related columns and trim to only variables needed
df_reshaped <- df_og %>% select(ppt_id, index_device_name, age_months, monk, ita, colnames(df_og[grepl("m[[:digit:]]_index_+", names(df_og))]), colnames(df_og[grepl("therm", names(df_og))]), colnames(df_og[grepl("m[[:digit:]]_ref_+", names(df_og))]), colnames(df_og[grepl("m[[:digit:]]_calm", names(df_og))]))
df_reshaped <- df_reshaped %>% select(-c(colnames(df_og[grepl("error", names(df_og))]), colnames(df_og[grepl("attempt", names(df_og))]), colnames(df_og[grepl("thb", names(df_og))])))
df_reshaped <- df_reshaped %>% select(-c(colnames(df_reshaped[grepl("confident", names(df_reshaped))])))
mdf_reshaped <- melt(df_reshaped, id.vars = c("ppt_id", "index_device_name", "age_months", "monk", "ita")) ## Melt df into long format, maintaining ID vars
mdf_reshaped$grp <- toupper(substr(mdf_reshaped$variable, start = 1, stop = 2)) # Extract measurement number into grouping variable
mdf_reshaped$mes <- substr(mdf_reshaped$variable, start = 4, stop = nchar(as.character(mdf_reshaped$variable))) # Extract index/ref and measurement type into variable
mdf_reshaped <- mdf_reshaped %>% select(-c(variable))
mdf_reshaped$mes <- ifelse(mdf_reshaped$mes=="therm_skin_temp", "ref_temp", mdf_reshaped$mes)
## Subset into index measurements only, further subset into each measurement type so value can be renamed accordingly
mdf_reshaped_i <- subset(mdf_reshaped, grepl("index", mdf_reshaped$mes))
mdf_reshaped_i_temp <- subset(mdf_reshaped_i, grepl("temp", mdf_reshaped_i$mes)) # Temp
names(mdf_reshaped_i_temp)[6] <- paste(mdf_reshaped_i_temp$mes)
mdf_reshaped_i_temp <- mdf_reshaped_i_temp %>% select(-c(mes))
mdf_reshaped_i_o2 <- subset(mdf_reshaped_i, grepl("_o2", mdf_reshaped_i$mes)) # O2
names(mdf_reshaped_i_o2)[6] <- paste(mdf_reshaped_i_o2$mes)
mdf_reshaped_i_o2 <- mdf_reshaped_i_o2 %>% select(-c(mes))
mdf_reshaped_i_pr <- subset(mdf_reshaped_i, grepl("pr", mdf_reshaped_i$mes)) # PR
names(mdf_reshaped_i_pr)[6] <- paste(mdf_reshaped_i_pr$mes)
mdf_reshaped_i_pr <- mdf_reshaped_i_pr %>% select(-c(mes))
mdf_reshaped_i_pi <- subset(mdf_reshaped_i, grepl("pi", mdf_reshaped_i$mes)) # PI
names(mdf_reshaped_i_pi)[6] <- paste(mdf_reshaped_i_pi$mes)
mdf_reshaped_i_pi <- mdf_reshaped_i_pi %>% select(-c(mes))
mdf_reshaped_i_rr <- subset(mdf_reshaped_i, grepl("rr", mdf_reshaped_i$mes)) # RR
names(mdf_reshaped_i_rr)[6] <- paste(mdf_reshaped_i_rr$mes)
mdf_reshaped_i_rr <- mdf_reshaped_i_rr %>% select(-c(mes))
## Join back to one df for recreation of full df
mdf_reshaped_i <- left_join(mdf_reshaped_i_temp, mdf_reshaped_i_o2, by = c("ppt_id", "index_device_name", "age_months", "monk", "ita", "grp"))
mdf_reshaped_i <- left_join(mdf_reshaped_i, mdf_reshaped_i_pr, by = c("ppt_id", "index_device_name", "age_months", "monk", "ita", "grp"))
mdf_reshaped_i <- left_join(mdf_reshaped_i, mdf_reshaped_i_pi, by = c("ppt_id", "index_device_name", "age_months", "monk", "ita", "grp"))
mdf_reshaped_i <- left_join(mdf_reshaped_i, mdf_reshaped_i_rr, by = c("ppt_id", "index_device_name", "age_months", "monk", "ita", "grp"))
## Do all of the above for reference measurements
mdf_reshaped_r <- subset(mdf_reshaped, grepl("ref", mdf_reshaped$mes))
mdf_reshaped_r_temp <- subset(mdf_reshaped_r, grepl("temp", mdf_reshaped_r$mes)) # Temp
names(mdf_reshaped_r_temp)[6] <- paste(mdf_reshaped_r_temp$mes)
mdf_reshaped_r_temp <- mdf_reshaped_r_temp %>% select(-c(mes))
mdf_reshaped_r_o2 <- subset(mdf_reshaped_r, grepl("_o2", mdf_reshaped_r$mes)) # O2
names(mdf_reshaped_r_o2)[6] <- paste(mdf_reshaped_r_o2$mes)
mdf_reshaped_r_o2 <- mdf_reshaped_r_o2 %>% select(-c(mes))
mdf_reshaped_r_pr <- subset(mdf_reshaped_r, grepl("pr", mdf_reshaped_r$mes)) # PR
names(mdf_reshaped_r_pr)[6] <- paste(mdf_reshaped_r_pr$mes)
mdf_reshaped_r_pr <- mdf_reshaped_r_pr %>% select(-c(mes))
mdf_reshaped_r_pi <- subset(mdf_reshaped_r, grepl("pi", mdf_reshaped_r$mes)) # PI
names(mdf_reshaped_r_pi)[6] <- paste(mdf_reshaped_r_pi$mes)
mdf_reshaped_r_pi <- mdf_reshaped_r_pi %>% select(-c(mes))
mdf_reshaped_r_rr <- subset(mdf_reshaped_r, grepl("rr", mdf_reshaped_r$mes)) # RR-all
mdf_reshaped_r_rrac <- subset(mdf_reshaped_r_rr, grepl("rracoustic", mdf_reshaped_r_rr$mes)) # RR-acoustic
names(mdf_reshaped_r_rrac)[6] <- paste(mdf_reshaped_r_rrac$mes)
mdf_reshaped_r_rr <- subset(mdf_reshaped_r_rr, !grepl("rracoustic", mdf_reshaped_r_rr$mes)) # RR
names(mdf_reshaped_r_rr)[6] <- paste(mdf_reshaped_r_rr$mes)
mdf_reshaped_r_rr <- mdf_reshaped_r_rr %>% select(-c(mes))
mdf_reshaped_r_rrac <- mdf_reshaped_r_rrac %>% select(-c(mes))
## Join back to one df for recreation of full df
mdf_reshaped_r <- left_join(mdf_reshaped_r_temp, mdf_reshaped_r_o2, by = c("ppt_id", "index_device_name", "age_months", "monk", "ita", "grp"))
mdf_reshaped_r <- left_join(mdf_reshaped_r, mdf_reshaped_r_pr, by = c("ppt_id", "index_device_name", "age_months", "monk", "ita", "grp"))
mdf_reshaped_r <- left_join(mdf_reshaped_r, mdf_reshaped_r_pi, by = c("ppt_id", "index_device_name", "age_months", "monk", "ita", "grp"))
mdf_reshaped_r <- left_join(mdf_reshaped_r, mdf_reshaped_r_rr, by = c("ppt_id", "index_device_name", "age_months", "monk", "ita", "grp"))
mdf_reshaped_r <- left_join(mdf_reshaped_r, mdf_reshaped_r_rrac, by = c("ppt_id", "index_device_name", "age_months", "monk", "ita", "grp"))
# Add calmness
mdf_reshaped_c <- subset(mdf_reshaped, grepl("calm", mdf_reshaped$mes)) # Calmness
names(mdf_reshaped_c)[6] <- paste(mdf_reshaped_c$mes)
mdf_reshaped_c <- mdf_reshaped_c %>% select(-c(mes))

# Join index and ref df's back to one melted df
mdf_reshaped <- left_join(mdf_reshaped_i, mdf_reshaped_r, by = c("ppt_id", "index_device_name", "age_months", "monk", "ita", "grp")) #long format df w/index & ref measurements for all devices & measurement types
mdf_reshaped <- left_join(mdf_reshaped, mdf_reshaped_c, by = c("ppt_id", "index_device_name", "age_months", "monk", "ita", "grp"))

# Center calmness to improve interpretability (mean = 3.596)
mdf_reshaped$calm2 <- mdf_reshaped$calm - 3.596

# Add indicator variables here for clinical thresholds (long format) -- Note: From the SAP, these are defined for the user in Section 5, if changed here be sure to change there and below
mdf_reshaped$index_hypoxic <- ifelse(mdf_reshaped$index_o2<90, 1, 0)
mdf_reshaped$ref_hypoxic <- ifelse(mdf_reshaped$ref_o2<90, 1, 0)
mdf_reshaped$index_fever <- ifelse(mdf_reshaped$index_temp>=37.5, 1, 0)
mdf_reshaped$ref_fever <- ifelse(mdf_reshaped$ref_temp>=37.5, 1, 0)
mdf_reshaped$index_fastbreath_12mo <- ifelse(mdf_reshaped$index_rr>49 & mdf_reshaped$age_months<12, 1, 0)
mdf_reshaped$ref_fastbreath_12mo <- ifelse(mdf_reshaped$ref_rr>49 & mdf_reshaped$age_months<12, 1, 0)
mdf_reshaped$refac_fastbreath_12mo <- ifelse(mdf_reshaped$ref_rracoustic>49 & mdf_reshaped$age_months<12, 1, 0)
mdf_reshaped$index_fastbreath_35mo <- ifelse(mdf_reshaped$index_rr>39 & (mdf_reshaped$age_months>11 & mdf_reshaped$age_months<36), 1, 0)
mdf_reshaped$ref_fastbreath_35mo <- ifelse(mdf_reshaped$ref_rr>39 & (mdf_reshaped$age_months>11 & mdf_reshaped$age_months<36), 1, 0)
mdf_reshaped$refac_fastbreath_35mo <- ifelse(mdf_reshaped$ref_rracoustic>39 & (mdf_reshaped$age_months>11 & mdf_reshaped$age_months<36), 1, 0)
mdf_reshaped$index_fastbreath_59mo <- ifelse(mdf_reshaped$index_rr>29 & (mdf_reshaped$age_months>35 & mdf_reshaped$age_months<60), 1, 0)
mdf_reshaped$ref_fastbreath_59mo <- ifelse(mdf_reshaped$ref_rr>29 & (mdf_reshaped$age_months>35 & mdf_reshaped$age_months<60), 1, 0)
mdf_reshaped$refac_fastbreath_59mo <- ifelse(mdf_reshaped$ref_rracoustic>29 & (mdf_reshaped$age_months>35 & mdf_reshaped$age_months<60), 1, 0)
mdf_reshaped$index_tachycardic_12mo <- ifelse(mdf_reshaped$index_pr>179 & mdf_reshaped$age_months<12, 1, 0)
mdf_reshaped$ref_tachycardic_12mo <- ifelse(mdf_reshaped$ref_pr>179 & mdf_reshaped$age_months<12, 1, 0)
mdf_reshaped$index_tachycardic_59mo <- ifelse(mdf_reshaped$index_pr>139 & mdf_reshaped$age_months>11, 1, 0)
mdf_reshaped$ref_tachycardic_59mo <- ifelse(mdf_reshaped$ref_pr>139 & mdf_reshaped$age_months>11, 1, 0)
## Add 3-level indicator variables for clinical thresholds (long format) -- Note: From the SAP, these are defined for the user in Section 5, if changed here be sure to change there and below
mdf_reshaped$index_hypoxic_tri <- case_when(mdf_reshaped$index_o2<88 ~ 2,
                                            mdf_reshaped$index_o2<90 & mdf_reshaped$index_o2>=88 ~ 1,
                                            mdf_reshaped$index_o2>=90 ~ 0)
mdf_reshaped$ref_hypoxic_tri <- case_when(mdf_reshaped$ref_o2<88 ~ 2,
                                            mdf_reshaped$ref_o2<90 & mdf_reshaped$ref_o2>=88 ~ 1,
                                            mdf_reshaped$ref_o2>=90 ~ 0)
mdf_reshaped$index_fever_tri <- case_when(mdf_reshaped$index_temp>=38.5 ~ 2,
                                            mdf_reshaped$index_temp<38.5 & mdf_reshaped$index_temp>=37.5 ~ 1,
                                            mdf_reshaped$index_temp<37.5 ~ 0)
mdf_reshaped$ref_fever_tri <- case_when(mdf_reshaped$ref_temp>=38.5 ~ 2,
                                            mdf_reshaped$ref_temp<38.5 & mdf_reshaped$ref_temp>=37.5 ~ 1,
                                            mdf_reshaped$ref_temp<37.5 ~ 0)
mdf_reshaped$index_fastbreath_12mo_tri <- case_when(mdf_reshaped$age_months<12 & mdf_reshaped$index_rr>55 ~ 2,
                                            mdf_reshaped$age_months<12 & mdf_reshaped$index_rr<=55 & mdf_reshaped$index_rr>=50 ~ 1,
                                            mdf_reshaped$age_months<12 & mdf_reshaped$index_rr<50 ~ 0)
mdf_reshaped$ref_fastbreath_12mo_tri <- case_when(mdf_reshaped$age_months<12 & mdf_reshaped$ref_rr>55 ~ 2,
                                            mdf_reshaped$age_months<12 & mdf_reshaped$ref_rr<=55 & mdf_reshaped$ref_rr>=50 ~ 1,
                                            mdf_reshaped$age_months<12 & mdf_reshaped$ref_rr<50 ~ 0)
mdf_reshaped$refac_fastbreath_12mo_tri <- case_when(mdf_reshaped$age_months<12 & mdf_reshaped$ref_rracoustic>55 ~ 2,
                                            mdf_reshaped$age_months<12 & mdf_reshaped$ref_rracoustic<=55 & mdf_reshaped$ref_rracoustic>=50 ~ 1,
                                            mdf_reshaped$age_months<12 & mdf_reshaped$ref_rracoustic<50 ~ 0)
mdf_reshaped$index_fastbreath_35mo_tri <- case_when(mdf_reshaped$age_months>11 & mdf_reshaped$age_months<36 & mdf_reshaped$index_rr>45 ~ 2,
                                            mdf_reshaped$age_months>11 & mdf_reshaped$age_months<36 & mdf_reshaped$index_rr<=45 & mdf_reshaped$index_rr>=40 ~ 1,
                                            mdf_reshaped$age_months>11 & mdf_reshaped$age_months<36 & mdf_reshaped$index_rr<40 ~ 0)
mdf_reshaped$ref_fastbreath_35mo_tri <- case_when(mdf_reshaped$age_months>11 & mdf_reshaped$age_months<36 & mdf_reshaped$ref_rr>45 ~ 2,
                                            mdf_reshaped$age_months>11 & mdf_reshaped$age_months<36 & mdf_reshaped$ref_rr<=45 & mdf_reshaped$ref_rr>=40 ~ 1,
                                            mdf_reshaped$age_months>11 & mdf_reshaped$age_months<36 & mdf_reshaped$ref_rr<40 ~ 0)
mdf_reshaped$refac_fastbreath_35mo_tri <- case_when(mdf_reshaped$age_months>11 & mdf_reshaped$age_months<36 & mdf_reshaped$ref_rracoustic>45 ~ 2,
                                            mdf_reshaped$age_months>11 & mdf_reshaped$age_months<36 & mdf_reshaped$ref_rracoustic<=45 & mdf_reshaped$ref_rracoustic>=40 ~ 1,
                                            mdf_reshaped$age_months>11 & mdf_reshaped$age_months<36 & mdf_reshaped$ref_rracoustic<40 ~ 0)
mdf_reshaped$index_fastbreath_59mo_tri <- case_when(mdf_reshaped$age_months>35 & mdf_reshaped$age_months<60 & mdf_reshaped$index_rr>35 ~ 2,
                                            mdf_reshaped$age_months>35 & mdf_reshaped$age_months<60 & mdf_reshaped$index_rr<=35 & mdf_reshaped$index_rr>=30 ~ 1,
                                            mdf_reshaped$age_months>35 & mdf_reshaped$age_months<60 & mdf_reshaped$index_rr<30 ~ 0)
mdf_reshaped$ref_fastbreath_59mo_tri <- case_when(mdf_reshaped$age_months>35 & mdf_reshaped$age_months<60 & mdf_reshaped$ref_rr>35 ~ 2,
                                            mdf_reshaped$age_months>35 & mdf_reshaped$age_months<60 & mdf_reshaped$ref_rr<=35 & mdf_reshaped$ref_rr>=30 ~ 1,
                                            mdf_reshaped$age_months>35 & mdf_reshaped$age_months<60 & mdf_reshaped$ref_rr<30 ~ 0)
mdf_reshaped$refac_fastbreath_59mo_tri <- case_when(mdf_reshaped$age_months>35 & mdf_reshaped$age_months<60 & mdf_reshaped$ref_rracoustic>35 ~ 2,
                                            mdf_reshaped$age_months>35 & mdf_reshaped$age_months<60 & mdf_reshaped$ref_rracoustic<=35 & mdf_reshaped$ref_rracoustic>=30 ~ 1,
                                            mdf_reshaped$age_months>35 & mdf_reshaped$age_months<60 & mdf_reshaped$ref_rracoustic<30 ~ 0)
mdf_reshaped$index_tachycardic_12mo_tri <- case_when(mdf_reshaped$age_months<12 & mdf_reshaped$index_pr>190 ~ 2,
                                            mdf_reshaped$age_months<12 & mdf_reshaped$index_pr<=190 & mdf_reshaped$index_pr>=180 ~ 1,
                                            mdf_reshaped$age_months<12 & mdf_reshaped$index_pr<180 ~ 0)
mdf_reshaped$ref_tachycardic_12mo_tri <- case_when(mdf_reshaped$age_months<12 & mdf_reshaped$ref_pr>190 ~ 2,
                                            mdf_reshaped$age_months<12 & mdf_reshaped$ref_pr<=190 & mdf_reshaped$ref_pr>=180 ~ 1,
                                            mdf_reshaped$age_months<12 & mdf_reshaped$ref_pr<180 ~ 0)
mdf_reshaped$index_tachycardic_59mo_tri <- case_when(mdf_reshaped$age_months>11 & mdf_reshaped$index_pr>150 ~ 2,
                                            mdf_reshaped$age_months>11 & mdf_reshaped$index_pr<=150 & mdf_reshaped$index_pr>=140 ~ 1,
                                            mdf_reshaped$age_months>11 & mdf_reshaped$index_pr<140 ~ 0)
mdf_reshaped$ref_tachycardic_59mo_tri <- case_when(mdf_reshaped$age_months>11 & mdf_reshaped$ref_pr>150 ~ 2,
                                            mdf_reshaped$age_months>11 & mdf_reshaped$ref_pr<=150 & mdf_reshaped$ref_pr>=140 ~ 1,
                                            mdf_reshaped$age_months>11 & mdf_reshaped$ref_pr<140 ~ 0)
# Add clinical age category for fast breathing, ensuring groupings fall within study age categories as well
mdf_reshaped$age_cat_fastbreathe <- case_when(mdf_reshaped$age_months<2 ~ "0-1 month",
                                              mdf_reshaped$age_months>1 & mdf_reshaped$age_months<12 ~ "2-11 months",
                                              mdf_reshaped$age_months>11 & mdf_reshaped$age_months<36 ~ "12-35 months",
                                              mdf_reshaped$age_months>35 ~ "36-59 months")
mdf_reshaped$grp <- as.factor(mdf_reshaped$grp)
# Add indicator variables for number of trials and number of successes for each clinical outcome to use in percent agreement section
mdf_reshaped$ref_index_pres_hypoxic <- ifelse(!is.na(mdf_reshaped$ref_hypoxic) & !is.na(mdf_reshaped$index_hypoxic), 1, 0)
mdf_reshaped$ref_index_agree_hypoxic <- ifelse(mdf_reshaped$ref_hypoxic==mdf_reshaped$index_hypoxic, 1, 0)
mdf_reshaped$ref_index_pres_fever <- ifelse(!is.na(mdf_reshaped$ref_fever) & !is.na(mdf_reshaped$index_fever), 1, 0)
mdf_reshaped$ref_index_agree_fever <- ifelse(mdf_reshaped$ref_fever==mdf_reshaped$index_fever, 1, 0)
mdf_reshaped$ref_index_pres_fb12mo <- ifelse(!is.na(mdf_reshaped$ref_fastbreath_12mo) & !is.na(mdf_reshaped$index_fastbreath_12mo), 1, 0)
mdf_reshaped$ref_index_agree_fb12mo <- ifelse(mdf_reshaped$ref_fastbreath_12mo==mdf_reshaped$index_fastbreath_12mo, 1, 0)
mdf_reshaped$ref_index_pres_fb35mo <- ifelse(!is.na(mdf_reshaped$ref_fastbreath_35mo) & !is.na(mdf_reshaped$index_fastbreath_35mo), 1, 0)
mdf_reshaped$ref_index_agree_fb35mo <- ifelse(mdf_reshaped$ref_fastbreath_35mo==mdf_reshaped$index_fastbreath_35mo, 1, 0)
mdf_reshaped$ref_index_pres_fb59mo <- ifelse(!is.na(mdf_reshaped$ref_fastbreath_59mo) & !is.na(mdf_reshaped$index_fastbreath_59mo), 1, 0)
mdf_reshaped$ref_index_agree_fb59mo <- ifelse(mdf_reshaped$ref_fastbreath_59mo==mdf_reshaped$index_fastbreath_59mo, 1, 0)
mdf_reshaped$refac_index_pres_fb12mo <- ifelse(!is.na(mdf_reshaped$refac_fastbreath_12mo) & !is.na(mdf_reshaped$index_fastbreath_12mo), 1, 0)
mdf_reshaped$refac_index_agree_fb12mo <- ifelse(mdf_reshaped$refac_fastbreath_12mo==mdf_reshaped$index_fastbreath_12mo, 1, 0)
mdf_reshaped$refac_index_pres_fb35mo <- ifelse(!is.na(mdf_reshaped$refac_fastbreath_35mo) & !is.na(mdf_reshaped$index_fastbreath_35mo), 1, 0)
mdf_reshaped$refac_index_agree_fb35mo <- ifelse(mdf_reshaped$refac_fastbreath_35mo==mdf_reshaped$index_fastbreath_35mo, 1, 0)
mdf_reshaped$refac_index_pres_fb59mo <- ifelse(!is.na(mdf_reshaped$refac_fastbreath_59mo) & !is.na(mdf_reshaped$index_fastbreath_59mo), 1, 0)
mdf_reshaped$refac_index_agree_fb59mo <- ifelse(mdf_reshaped$refac_fastbreath_59mo==mdf_reshaped$index_fastbreath_59mo, 1, 0)
mdf_reshaped$ref_index_pres_tachy12mo <- ifelse(!is.na(mdf_reshaped$ref_tachycardic_12mo) & !is.na(mdf_reshaped$index_tachycardic_12mo), 1, 0)
mdf_reshaped$ref_index_agree_tachy12mo <- ifelse(mdf_reshaped$ref_tachycardic_12mo==mdf_reshaped$index_tachycardic_12mo, 1, 0)
mdf_reshaped$ref_index_pres_tachy59mo <- ifelse(!is.na(mdf_reshaped$ref_tachycardic_59mo) & !is.na(mdf_reshaped$index_tachycardic_59mo), 1, 0)
mdf_reshaped$ref_index_agree_tachy59mo <- ifelse(mdf_reshaped$ref_tachycardic_59mo==mdf_reshaped$index_tachycardic_59mo, 1, 0)
mdf_reshaped$ref_refac_pres_fb12mo <- ifelse(!is.na(mdf_reshaped$ref_fastbreath_12mo) & !is.na(mdf_reshaped$refac_fastbreath_12mo), 1, 0) # Annotated RR vs. RRac
mdf_reshaped$ref_refac_agree_fb12mo <- ifelse(mdf_reshaped$ref_fastbreath_12mo==mdf_reshaped$refac_fastbreath_12mo, 1, 0)
mdf_reshaped$ref_refac_pres_fb35mo <- ifelse(!is.na(mdf_reshaped$ref_fastbreath_35mo) & !is.na(mdf_reshaped$refac_fastbreath_35mo), 1, 0)
mdf_reshaped$ref_refac_agree_fb35mo <- ifelse(mdf_reshaped$ref_fastbreath_35mo==mdf_reshaped$refac_fastbreath_35mo, 1, 0)
mdf_reshaped$ref_refac_pres_fb59mo <- ifelse(!is.na(mdf_reshaped$ref_fastbreath_59mo) & !is.na(mdf_reshaped$refac_fastbreath_59mo), 1, 0)
mdf_reshaped$ref_refac_agree_fb59mo <- ifelse(mdf_reshaped$ref_fastbreath_59mo==mdf_reshaped$refac_fastbreath_59mo, 1, 0)
# Do the same for trinary variables
mdf_reshaped$ref_index_pres_hypoxic_tri <- ifelse(!is.na(mdf_reshaped$ref_hypoxic_tri) & !is.na(mdf_reshaped$index_hypoxic_tri), 1, 0)
mdf_reshaped$ref_index_agree_hypoxic_tri <- ifelse(mdf_reshaped$ref_hypoxic_tri==mdf_reshaped$index_hypoxic_tri, 1, 0)
mdf_reshaped$ref_index_pres_fever_tri <- ifelse(!is.na(mdf_reshaped$ref_fever_tri) & !is.na(mdf_reshaped$index_fever_tri), 1, 0)
mdf_reshaped$ref_index_agree_fever_tri <- ifelse(mdf_reshaped$ref_fever_tri==mdf_reshaped$index_fever_tri, 1, 0)
mdf_reshaped$ref_index_pres_fb12mo_tri <- ifelse(!is.na(mdf_reshaped$ref_fastbreath_12mo_tri) & !is.na(mdf_reshaped$index_fastbreath_12mo_tri), 1, 0)
mdf_reshaped$ref_index_agree_fb12mo_tri <- ifelse(mdf_reshaped$ref_fastbreath_12mo_tri==mdf_reshaped$index_fastbreath_12mo_tri, 1, 0)
mdf_reshaped$ref_index_pres_fb35mo_tri <- ifelse(!is.na(mdf_reshaped$ref_fastbreath_35mo_tri) & !is.na(mdf_reshaped$index_fastbreath_35mo_tri), 1, 0)
mdf_reshaped$ref_index_agree_fb35mo_tri <- ifelse(mdf_reshaped$ref_fastbreath_35mo_tri==mdf_reshaped$index_fastbreath_35mo_tri, 1, 0)
mdf_reshaped$ref_index_pres_fb59mo_tri <- ifelse(!is.na(mdf_reshaped$ref_fastbreath_59mo_tri) & !is.na(mdf_reshaped$index_fastbreath_59mo_tri), 1, 0)
mdf_reshaped$ref_index_agree_fb59mo_tri <- ifelse(mdf_reshaped$ref_fastbreath_59mo_tri==mdf_reshaped$index_fastbreath_59mo_tri, 1, 0)
mdf_reshaped$refac_index_pres_fb12mo_tri <- ifelse(!is.na(mdf_reshaped$refac_fastbreath_12mo_tri) & !is.na(mdf_reshaped$index_fastbreath_12mo_tri), 1, 0)
mdf_reshaped$refac_index_agree_fb12mo_tri <- ifelse(mdf_reshaped$refac_fastbreath_12mo_tri==mdf_reshaped$index_fastbreath_12mo_tri, 1, 0)
mdf_reshaped$refac_index_pres_fb35mo_tri <- ifelse(!is.na(mdf_reshaped$refac_fastbreath_35mo_tri) & !is.na(mdf_reshaped$index_fastbreath_35mo_tri), 1, 0)
mdf_reshaped$refac_index_agree_fb35mo_tri <- ifelse(mdf_reshaped$refac_fastbreath_35mo_tri==mdf_reshaped$index_fastbreath_35mo_tri, 1, 0)
mdf_reshaped$refac_index_pres_fb59mo_tri <- ifelse(!is.na(mdf_reshaped$refac_fastbreath_59mo_tri) & !is.na(mdf_reshaped$index_fastbreath_59mo_tri), 1, 0)
mdf_reshaped$refac_index_agree_fb59mo_tri <- ifelse(mdf_reshaped$refac_fastbreath_59mo_tri==mdf_reshaped$index_fastbreath_59mo_tri, 1, 0)
mdf_reshaped$ref_index_pres_tachy12mo_tri <- ifelse(!is.na(mdf_reshaped$ref_tachycardic_12mo_tri) & !is.na(mdf_reshaped$index_tachycardic_12mo_tri), 1, 0)
mdf_reshaped$ref_index_agree_tachy12mo_tri <- ifelse(mdf_reshaped$ref_tachycardic_12mo_tri==mdf_reshaped$index_tachycardic_12mo_tri, 1, 0)
mdf_reshaped$ref_index_pres_tachy59mo_tri <- ifelse(!is.na(mdf_reshaped$ref_tachycardic_59mo_tri) & !is.na(mdf_reshaped$index_tachycardic_59mo_tri), 1, 0)
mdf_reshaped$ref_index_agree_tachy59mo_tri <- ifelse(mdf_reshaped$ref_tachycardic_59mo_tri==mdf_reshaped$index_tachycardic_59mo_tri, 1, 0)
mdf_reshaped$ref_refac_pres_fb12mo_tri <- ifelse(!is.na(mdf_reshaped$ref_fastbreath_12mo_tri) & !is.na(mdf_reshaped$refac_fastbreath_12mo_tri), 1, 0) # Annotated RR vs. RRac
mdf_reshaped$ref_refac_agree_fb12mo_tri <- ifelse(mdf_reshaped$ref_fastbreath_12mo_tri==mdf_reshaped$refac_fastbreath_12mo_tri, 1, 0)
mdf_reshaped$ref_refac_pres_fb35mo_tri <- ifelse(!is.na(mdf_reshaped$ref_fastbreath_35mo_tri) & !is.na(mdf_reshaped$refac_fastbreath_35mo_tri), 1, 0)
mdf_reshaped$ref_refac_agree_fb35mo_tri <- ifelse(mdf_reshaped$ref_fastbreath_35mo_tri==mdf_reshaped$refac_fastbreath_35mo_tri, 1, 0)
mdf_reshaped$ref_refac_pres_fb59mo_tri <- ifelse(!is.na(mdf_reshaped$ref_fastbreath_59mo_tri) & !is.na(mdf_reshaped$refac_fastbreath_59mo_tri), 1, 0)
mdf_reshaped$ref_refac_agree_fb59mo_tri <- ifelse(mdf_reshaped$ref_fastbreath_59mo_tri==mdf_reshaped$refac_fastbreath_59mo_tri, 1, 0)

# Step 2: Create device df's
## Long format (M1-M3 are levels of one variable)
df_radg_l <- subset(mdf_reshaped, index_device_name=="Rad-G Temp (Masimo)")
df_bio_l <- subset(mdf_reshaped, index_device_name=="m800 (Biolight)")
df_neo_l <- subset(mdf_reshaped, index_device_name=="NeoGuard (Neopenda)")
df_onyx_l <- subset(mdf_reshaped, index_device_name=="Onyx PO+RR (Nonin)")
df_scan_l <- subset(mdf_reshaped, index_device_name=="Scanbo v8 (Scanbo)")
```

This is a companion document to the TIMCI Diagnostic Accuracy Study Data Analysis at the global level. This document has been prepared to assess the effect of skin tone on index device measurement. A linear mixed effects regression is constructed in the form of 'index device result ~ skin tone + age in months + calmness' to control for repeated measures across all devices and clinical measurements. Calmness is centered around the mean with negative coefficients reflecting more agitation and positive coefficients reflecting more calmness. Monk skin tone is also compared against the calculated individual typography angle (based on colorimeter readings) in contingency table formatting and evaluated using Fisher's exact test with an intrinsic Monte Carlo simulation to calculate p-values due to low cell counts.

```{r lmer_setup, echo=FALSE, include=FALSE}
# Define parameters applicable to all sections
## Covariates and predictors
covariates <- "+age_months+calm2+"
predictor1 <- "monk"
predictor2 <- "ita"

## Labels for regression outputs
labels1 <- c("Monk skin tone", "Age in months", "Calmness")
labels2 <- c("ITA", "Age in Months", "Calmness")
```

# Using Monk Skin Tone
## Measurement of SpO2
```{r}
# Define title, outcome, and model
title <- "Effect of Monk Skin Tone on SpO2 Measurement across Index Devices"
outcome <- "index_o2"
fml <- paste(outcome, "~", predictor1, covariates, "(1|ppt_id)", sep = "")

# Build models using different device df's
mo2_radg <- lmer(fml, data = df_radg_l)
mo2_neo <- lmer(fml, data = df_neo_l)
mo2_scan <- lmer(fml, data = df_scan_l)
mo2_bio <- lmer(fml, data = df_bio_l)
mo2_onyx <- lmer(fml, data = df_onyx_l)

# Format output
stargazer(mo2_radg,mo2_neo, mo2_scan,mo2_bio, mo2_onyx,
                type = "text",
                ci = TRUE,
                title = title,
                covariate.labels = labels1,
                column.labels = c("Rad-G", "Neopenda", "Scanbo", "Biolight", "Onyx"),
                dep.var.labels = "SpO2")
```

## Measurement of Temperature
```{r}
# Define title, outcome, and model
title <- "Effect of Monk Skin Tone on Temperature Measurement across Index Devices"
outcome <- "index_temp"
fml <- paste(outcome, "~", predictor1, covariates, "(1|ppt_id)", sep = "")

# Build models using different device df's
mtemp_radg <- lmer(fml, data = df_radg_l)
mtemp_neo <- lmer(fml, data = df_neo_l)
mtemp_scan <- lmer(fml, data = df_scan_l)

# Format output
stargazer(mtemp_radg,mtemp_neo, mtemp_scan,
                type = "text",
                title = title,
                covariate.labels = labels1,
                column.labels = c("Rad-G", "Neopenda", "Scanbo"),
                dep.var.labels = "Temperature")
```

## Measurement of Pulse Rate
```{r}
# Define title, outcome, and model
title <- "Effect of Monk Skin Tone on Pulse Rate Measurement across Index Devices"
outcome <- "index_pr"
fml <- paste(outcome, "~", predictor1, covariates, "(1|ppt_id)", sep = "")

# Build models using different device df's
mpr_radg <- lmer(fml, data = df_radg_l)
mpr_neo <- lmer(fml, data = df_neo_l)
mpr_scan <- lmer(fml, data = df_scan_l)
mpr_bio <- lmer(fml, data = df_bio_l)
mpr_onyx <- lmer(fml, data = df_onyx_l)

# Format output
stargazer(mpr_radg,mpr_neo, mpr_scan,mpr_bio, mpr_onyx,
                type = "text",
                title = title,
                covariate.labels = labels1,
                column.labels = c("Rad-G", "Neopenda", "Scanbo", "Biolight", "Onyx"),
                dep.var.labels = "Pulse Rate")
```

## Measurement of Respiratory Rate
```{r}
# Define title, outcome, and model
title <- "Effect of Monk Skin Tone on Respiratory Rate Measurement across Index Devices"
outcome <- "index_rr"
fml <- paste(outcome, "~", predictor1, covariates, "(1|ppt_id)", sep = "")

# Build models using different device df's
mrr_radg <- lmer(fml, data = df_radg_l)
mrr_neo <- lmer(fml, data = df_neo_l)
mrr_scan <- lmer(fml, data = df_scan_l)
mrr_bio <- lmer(fml, data = df_bio_l)
mrr_onyx <- lmer(fml, data = df_onyx_l)

# Format output
stargazer(mrr_radg,mrr_neo, mrr_scan,mrr_bio, mrr_onyx,
                type = "text",
                title = title,
                covariate.labels = labels1,
                column.labels = c("Rad-G", "Neopenda", "Scanbo", "Biolight", "Onyx"),
                dep.var.labels = "Respiratory Rate")
```

# Using Individual Typography Angle
## Measurement of SpO2
```{r}
# Define title, outcome, and model
title <- "Effect of ITA on SpO2 Measurement across Index Devices"
outcome <- "index_o2"
fml <- paste(outcome, "~", predictor2, covariates, "(1|ppt_id)", sep = "")

# Build models using different device df's
mo2_radg <- lmer(fml, data = df_radg_l)
mo2_neo <- lmer(fml, data = df_neo_l)
mo2_scan <- lmer(fml, data = df_scan_l)
mo2_bio <- lmer(fml, data = df_bio_l)
mo2_onyx <- lmer(fml, data = df_onyx_l)

# Format output
stargazer(mo2_radg,mo2_neo, mo2_scan,mo2_bio, mo2_onyx,
                type = "text",
                title = title,
                covariate.labels = labels2,
                column.labels = c("Rad-G", "Neopenda", "Scanbo", "Biolight", "Onyx"),
                dep.var.labels = "SpO2")
```

## Measurement of Temperature
```{r}
# Define title, outcome, and model
title <- "Effect of ITA on Temperature Measurement across Index Devices"
outcome <- "index_temp"
fml <- paste(outcome, "~", predictor2, covariates, "(1|ppt_id)", sep = "")

# Build models using different device df's
mtemp_radg <- lmer(fml, data = df_radg_l)
mtemp_neo <- lmer(fml, data = df_neo_l)
mtemp_scan <- lmer(fml, data = df_scan_l)

# Format output
stargazer(mtemp_radg,mtemp_neo, mtemp_scan,
                type = "text",
                title = title,
                covariate.labels = labels2,
                column.labels = c("Rad-G", "Neopenda", "Scanbo"),
                dep.var.labels = "Temperature")
```

## Measurement of Pulse Rate
```{r}
# Define title, outcome, and model
title <- "Effect of ITA on Pulse Rate Measurement across Index Devices"
outcome <- "index_pr"
fml <- paste(outcome, "~", predictor2, covariates, "(1|ppt_id)", sep = "")

# Build models using different device df's
mpr_radg <- lmer(fml, data = df_radg_l)
mpr_neo <- lmer(fml, data = df_neo_l)
mpr_scan <- lmer(fml, data = df_scan_l)
mpr_bio <- lmer(fml, data = df_bio_l)
mpr_onyx <- lmer(fml, data = df_onyx_l)

# Format output
stargazer(mpr_radg,mpr_neo, mpr_scan,mpr_bio, mpr_onyx,
                type = "text",
                title = title,
                covariate.labels = labels2,
                column.labels = c("Rad-G", "Neopenda", "Scanbo", "Biolight", "Onyx"),
                dep.var.labels = "Pulse Rate")
```

## Measurement of Respiratory Rate
```{r}
# Define title, outcome, and model
title <- "Effect of ITA on Respiratory Rate Measurement across Index Devices"
outcome <- "index_rr"
fml <- paste(outcome, "~", predictor2, covariates, "(1|ppt_id)", sep = "")

# Build models using different device df's
mrr_radg <- lmer(fml, data = df_radg_l)
mrr_neo <- lmer(fml, data = df_neo_l)
mrr_scan <- lmer(fml, data = df_scan_l)
mrr_bio <- lmer(fml, data = df_bio_l)
mrr_onyx <- lmer(fml, data = df_onyx_l)

# Format output
stargazer(mrr_radg,mrr_neo, mrr_scan,mrr_bio, mrr_onyx,
                type = "text",
                title = title,
                covariate.labels = labels2,
                column.labels = c("Rad-G", "Neopenda", "Scanbo", "Biolight", "Onyx"),
                dep.var.labels = "Respiratory Rate")
```

# Monk Skin Tone vs. Individual Typography Angle
```{r}
tdf <- df_og %>% select(ppt_id, monk, ita)
tdf <- tdf %>% mutate(ita_cat = 
                        case_when(ita>55 ~ "Very light",
                         ita<=55 & ita>=41 ~ "Light",
                         ita<41 & ita>=28 ~ "Intermediate",
                         ita<28 & ita>=10 ~ "Tan",
                         ita<10 & ita>= -30 ~ "Brown",
                         ita< -30 ~ "Dark"),
                      monk_cat = 
                        case_when(monk==1 ~ "A",
                                  monk==2 ~ "B",
                                  monk==3 ~ "C",
                                  monk==4 ~ "D",
                                  monk==5 ~ "E",
                                  monk==6 ~ "F",
                                  monk==7 ~ "G",
                                  monk==8 ~ "H",
                                  monk==9 ~ "I",
                                  monk==10 ~ "J",
                                  monk>10 ~ NA)
)
tdf$ita_cat <- factor(tdf$ita_cat, levels = c("Dark", "Brown", "Tan", "Very light"))
cat.table <- table(tdf$monk_cat, tdf$ita_cat)
```
`r knitr::kable(cat.table)`

```{r}
stats::fisher.test(cat.table, hybrid = T, simulate.p.value = T)
```

